### 2014-09-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix typo

\item The third exterior fuel item included the wood on the basement balcony and siding. To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data abotu the ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes. The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.

>>>>

\item The third exterior fuel item included the wood on the basement balcony and siding. To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about the ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes. The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
